Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-12-18 src/tf-cutcell-comparison/responses2.tex
improve motivation for TF tracer advection test

\begin{quotation}
 Lines 321-322 – When the flow is aligned with the grid there is no cross coordinate 
 flow and therefore the numerics are essentially reduced to a one-dimensional 
 advection equation. I don't see how grid distortion is even an issue. 
\end{quotation}
The advection scheme fits a multidimensional polynomial using a stencil of cell centroids, hence grid distortions will affect the resulting least squares fit.  If the test used a dimensionally-split advection scheme with a terrain-following coordinate transform, then the test would indeed reduce to a one-dimensional problem.  \TODO{clarify in the manuscript}

>>>>

\begin{quotation}
 Lines 321-322 – When the flow is aligned with the grid there is no cross coordinate 
 flow and therefore the numerics are essentially reduced to a one-dimensional 
 advection equation. I don't see how grid distortion is even an issue. 
\end{quotation}
The advection scheme fits a multidimensional polynomial using a stencil of cell centroids, hence grid distortions could affect the resulting least squares fit.  If the test used a dimensionally-split advection scheme with a terrain-following coordinate transform, then the test would indeed reduce to a one-dimensional problem.  We have provided a more detailed motivation of this test in the introductory paragraph starting at line \TODO{xxx}.

### 2015-12-18 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
improve motivation for TF tracer advection test

\subsection{Terrain following advection}
In the horizontal advection test, results were least accurate on the BTF grid, where the grid was most non-orthogonal and flow was misaligned with the grid layers.  Here, we formulate a new tracer advection test in which the velocity field is everywhere tangential to the basic terrain following coordinate surfaces.  This test determines whether the primary source of numerical error is due to non-orthogonality or misalignment of the flow with grid layers.  \TODO{explain how grid distortion could reduce accuracy of the advection scheme}

>>>>

\subsection{Terrain following advection}
In the horizontal advection test, results were least accurate on the BTF grid, where the grid was most non-orthogonal and flow was misaligned with the grid layers.  Here, we formulate a new tracer advection test in which the velocity field is everywhere tangential to the basic terrain following coordinate surfaces.
On the BTF grid, the flow is then aligned with the grid, but the data in the multidimensional advection stencil is not uniformly distributed because the BTF grid is non-orthogonal.
Conversely, on the cut cell grid, the flow is misaligned with the grid but, except in the lowest layer, the grid is orthogonal.
This test determines whether the primary source of numerical error is due to non-orthogonality or misalignment of the flow with grid layers.
